---
output: github_document
editor_options: 
  chunk_output_type: console
  markdown: 
    wrap: 72
always_allow_html: true
---


```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment  = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
**Hard Test Solution -- Shiny App Deployment as an R Package**

Evaluating Mentor: Marlon Cobos
Student: Mariana Castaneda Guzman
Last updated: 2026-02-23


## Overview

`hard_test_solution` is a minimal R package that deploys an interactive Shiny
application demonstrating a reproducible geospatial workflow using
WorldClim bioclimatic data.

The application performs the following steps:

1.  Downloads WorldClim global bioclimatic variables
2.  Extracts a selected BIO variable (default = BIO1)
3.  Crops the raster to South America
4.  Masks the raster using a South America boundary shapefile
5.  Visualizes the raster at each processing step

The processing workflow is handled by `helper_bio()`, while `run_app()`
launches the Shiny interface.



## Installation

Install the development version from GitHub:

```{r , message=FALSE, warning=FALSE}
# install.packages("remotes")
remotes::install_github("castanedaM/nicheR_GSoC_2026_test_solutions/hard_test_solution")
```

## Usage

Launch the Shiny application:

```{r eval=FALSE, include=TRUE}
hard_test_solution::run_app()
```

Run the processing workflow directly:

``` {r}
out <- hard_test_solution::helper_bio(selected_bio = 1)
names(out)

terra::plot(out$bio_masked)
```

## Package Contents

-   `run_app()` - Launches the Shiny interface
-   `helper_bio()` - Downloads and processes WorldClim bioclimatic
    data
-   roxygen2 documentation
-   DESCRIPTION file
-   MIT License
-   GitHub Actions configured to pass `R CMD check`


