---
title: "README"
author: "Mariana Castaneda"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
**Hard Test Solution -- Shiny App Deployment as an R Package**\
Evaluating Mentor: Marlon Cobos\
Student: Mariana Castaneda Guzman\
Last updated: 2026-02-12


## Overview

`hts` is a minimal R package that deploys an interactive Shiny
application demonstrating a reproducible geospatial workflow using
WorldClim bioclimatic data.

The application performs the following steps:

1.  Downloads WorldClim global bioclimatic variables\
2.  Extracts a selected BIO variable (default = BIO1)\
3.  Crops the raster to South America\
4.  Masks the raster using a South America boundary shapefile\
5.  Visualizes the raster at each processing step

The processing workflow is handled by `helper_bio()`, while `run_app()`
launches the Shiny interface.



## Installation

Install the development version from GitHub:

``` {r}
# install.packages("remotes")
remotes::install_github("castanedaM/hts")
```

## Usage

Launch the Shiny application:

``` {r}
hts::run_app()
```

Run the processing workflow directly:

``` {r}
out <- hts::helper_bio(selected_bio = 1)
plot(out$bio_masked)
```

## Package Contents

-   `run_app()` -- Launches the Shiny interface\
-   `helper_bio()` -- Downloads and processes WorldClim bioclimatic
    data\
-   roxygen2 documentation\
-   DESCRIPTION file\
-   MIT License\
-   GitHub Actions configured to pass `R CMD check`


## License
MIT License
