---
output: github_document
editor_options: 
  chunk_output_type: console
  markdown: 
    wrap: 72
always_allow_html: true
---


```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment  = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```



# Hard Test Solution -- Shiny App as an R Package

Evaluating Mentor: Marlon Cobos

Student: Mariana Castaneda Guzman

Last updated: 2026-03-05


## Test Promt: 

1. Create an R package that deploys the Shiny app developed above.

2. Include:

   - A function (e.g., `run_app()`) to launch the interface  
   - Helper functions for downloading and processing bioclim data  
   - Documentation using `roxygen2`  
   - A `DESCRIPTION` file and license  
   - A `README` with installation and usage instructions  
   - GitHub Actions configured to run `R CMD check` with no errors, warnings, or notes  

## Overview

`HardTestSolution` is a minimal R package that deploys an interactive Shiny
application demonstrating a reproducible geospatial workflow using
WorldClim bioclimatic data.

The application performs the following steps:

1.  Downloads WorldClim global bioclimatic variables
2.  Extracts a selected BIO variable (default = BIO1)
3.  Crops the raster to selected region (default = South America)
4.  Masks the raster using a the region boundary
5.  Visualizes the raster at each processing step

The processing workflow is handled by `helper_bio()`, while `run_app()`
launches the Shiny interface.



## Installation

Install the development version from GitHub:

```{r message=FALSE, warning=FALSE, include=FALSE}
# install.packages("remotes")
remotes::install_github("castanedaM/nicheR_GSoC_2026_test_solutions/HardTestSolution")
```

```{r eval = FALSE, include=TRUE}
# install.packages("remotes")
remotes::install_github("castanedaM/nicheR_GSoC_2026_test_solutions/HardTestSolution")
```

## Usage

Launch the Shiny application:

```{r eval=FALSE, include=TRUE}
HardTestSolution::run_app()
```

If selected bio was `bio = 1` and `region = Asia`

```{r echo=FALSE}
out <- HardTestSolution::helper_bio(bio = 1, region = "Asia")

terra::plot(out$bio_stack)
terra::plot(out$bio, main = "BIO 1")
terra::plot(out$bio_cropped, main = "BIO 1 cropped")
terra::plot(out$bio_masked, main = "BIO 1 cropped + masked")
```

## Package Contents

-   `run_app()` - Launches the Shiny interface
-   `helper_bio()` - Downloads and processes WorldClim bioclimatic
    data
-   roxygen2 documentation
-   DESCRIPTION file
-   MIT License
-   GitHub Actions configured to pass `R CMD check`

<!-- badges: start -->
[![R-CMD-check](https://github.com/castanedaM/nicheR_GSoC_2026_test_solutions/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/castanedaM/nicheR_GSoC_2026_test_solutions/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->


